%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy_resume}
\usepackage{fancyhdr}
\usepackage{comment}
\usepackage{enumitem}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{James}{Parsons}{ 
\urlstyle{same}
\href{mailto:jwparsons@pm.me}{jwparsons@pm.me} | 305.282.0009 |
\href{jwparsons.bitbucket.io}{jwparsons.bitbucket.io}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{Florida State University}
\descript{MS in Computer Science}
\location{Aug 2018 | Tallahassee, FL}
College of Arts \& Sciences\\
\location{GPA: 4.0}
\sectionsep

\subsection{Boston University}
\descript{BS in Biomedical Engineering}
\location{May 2015 | Boston, MA}
College of Engineering \\
\location{GPA: 3.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/jwparsons}{\bf jwparsons} \\
BitBucket://\href{https://bitbucket.org/jwparsons/}{\bf jwparsons} \\
LinkedIn://  \href{https://www.linkedin.com/in/jamespar/}{\bf jamespar} \\
StackOverflow://\href{https://stackoverflow.com/users/9915449/jwp}{\bf jwp}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Social Network Mining \\
Artificial Intelligence \\
Wireless \& Mobile Computing \\
Data Communications \\
Parallel Programming \\
Theory of Automata \\
Cyber Security Fundamentals \\
Network Security \\
\sectionsep

\subsection{Undergraduate}
Data Structures \\
Algorithms \\
Operating Systems \\
Theory of Computation \\
Theory \& Structure of Databases \\
Computer Organization \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Skilled:}
C++ \textbullet{} Python \textbullet{} Swift \textbullet{} iOS \textbullet{} Unreal \\
\textbullet{} Git \\
\location{Knowledgable:}
C\# \textbullet{} Java \textbullet{} Unity \textbullet{} Android \textbullet{} \LaTeX\ \\
Unix \textbullet{} Mercurial \\
\location{Familiar:}
C \textbullet{} Azure \textbullet{} JavaScript \textbullet{} HTML\textbullet{} CSS \\ Assembly \textbullet{} TensorFlow \textbullet{} Turi Create \\ NodeJS \textbullet{} Matlab \textbullet{} Perforce \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{E-Crime Inv. Tech. Lab}
\descript{| Grad. Research Assistant}
\location{Jan 2017 – May 2018 | Tallahassee, FL}
\begin{itemize}[noitemsep,topsep=0pt]
\item Collaborated with a team of 11 people to develop an iOS machine learning data extraction application for law enforcement.
\item Programmed 3 data extraction systems based on computer vision and file meta-data analysis using Swift.
\item Researched, designed, and implemented 7+ iterations of a novel wordbreaking (NLP) algorithm using Python (w/ NLTK).
\end{itemize}
\vspace{3mm}

\runsubsection{Covalent Reality}
\descript{| Virtual Reality Development Intern}
\location{Jun 2016 – May 2017 | Tallahassee, FL}
\begin{itemize}[noitemsep,topsep=0pt]
\item Led the development of 3 custom VR experiences using UE4 (C++) and Unity 3D (C\#).
\item Developed a VR architectural visualization template using UE4 (Blueprints) to reduce project initialization labor by \~{}90\%.
\item Created video tutorials and hosted weekly seminars to help new hires learn various aspects of VR development.
\end{itemize}
\vspace{3mm}

\runsubsection{Florida State University}
\descript{| Grad. Teaching Assistant}
\location{Jan 2016 – May 2018 | Tallahassee, FL}
\begin{itemize}[noitemsep,topsep=0pt]
\itemsep0em 
\item Delivered lectures to classrooms of 50+ students.
\item Guided students through course material (Intro. to C++, OOP w/ C++) in recitations and office hours.
\end{itemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OPEN SOURCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Open Source}
\runsubsection{fresh script}
\descript{| Python}
\location{Oct 2018 - Present | Miami, FL}
A program to consolidate Spotify tracks posted in the HipHopHeads subreddit to a specified playlist. Increased track gathering capabilities by \~{}200\% by handling non-Spotify linked Reddit posts with NLP and Spotify API search.
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Rebound}
\descript{| Unreal Engine 4 + NodeJS}
\location{Sep 2017 - Dec 2017 | Tallahassee, FL}
Online multiplayer arena deathmatch video game (UE4) with a corresponding matchmaking server (NodeJS). Responsible for game design, UI/UX, mechanics, multiplayer support, and the matchmaking system.
\sectionsep

\runsubsection{DeepReads}
\descript{| TensorFlow}
\location{March 2018 – May 2018 | Tallahassee, FL}
Utilized the Goodeads API and recurrent neural networks (TF) to generate text descriptions of books by genre (Fantasy, Mystery, Philosophy, Romance, SciFi).
\sectionsep

\runsubsection{MeatCoin}
\descript{| NodeJS + Azure}
\location{Jan 2018 – Feb 2018 | Tallahassee, FL}
Text-based Cryptocurrency trading simulator for Discord. Invented for use among my friend group as a joke. At peak popularity, had 30+ people trading. Hosted on a Microsoft Azure VM.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{comment}
\section{Publications} 
\renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
\bibliographystyle{abbrv}
\bibliography{publications}
\nocite{*}
\end{comment}

\end{minipage} 
\end{document}  \documentclass[]{article}